---
title: "R Notebook"
output: html_notebook
---

- Read the Dataset!

```{r}
library(readr)
ice_cream_dataR <- as.data.frame(read_csv("ice_cream_dataR.csv"))
View(ice_cream_dataR)
```

### Cleaning

- Add a new chunk by clicking the *Insert Chunk* button on the toolbar and selecting *R* or by pressing *Ctrl+Alt+I*.
- Delete excess columns
```{r}
ice_cream_dataR$X4 <- NULL
ice_cream_dataR$X5 <- NULL
ice_cream_dataR$X6 <- NULL
ice_cream_dataR$X7 <- NULL

View(ice_cream_dataR)
```

- All fixed!
- Add new column where each flavor is grouped and the total number is in a column called "count"
- Remove columns with NA

```{r}

GraphData <- 
  ice_cream_dataR %>%
  group_by(flavor, cup_or_cone) %>% 
  summarise(total= n())

FinalGraphData <- na.omit(GraphData) 
View(FinalGraphData)
```


### Visualization
```{r}
library(DataComputing)

FlavorPlot <- ggplot(data=FinalGraphData,aes(x=reorder(flavor,total),y=total ,fill=cup_or_cone))+geom_bar(stat='identity',position='stack', width=.9) + theme(axis.text.x=element_text(angle=60,hjust=1))

FlavorPlot
```

###What are the top three flavors?

###Consider 1 is a cup and 0 is a cone. Which is more popular, if they are not equal?







